Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Edit mostly comments

\HEComment{the reason we need SVM fine grain and atomics may be better
discussed directly in the section on implementation?}

@@

\HEComment{given the paper title, maybe ``non-blocking'' would be more
  appropriate than ``non-persistent''?}

@@

\paragraph{Results} \ADComment{Discuss the results.}
\mytab~\ref{tab:nonpersistentworkload} illustrates the caracteristics
found for the three types of workloads. For the medium and heavy
workloads, the 40ms period corresponds to an execution every $25^{th}$
of seconds which coincide with the human persistence of vision. The
3ms execution duration of both light and medium configurations may
indicate a lower bound of GPU execution time for system workloads.

@@

\ADComment{Results for stand-alone vs.\ cooperative without co-scheduling.}

@@

Cooperative scheduling primitives entails an overhead even if no
killing, forking or resizing ever happen. We measure this overhead via
the execution time ratio between the original kernel and the
cooperative one, forcing the scheduler to never modify the number of
active workgroups. Since the cooperative kernel contains the
non-persistent task code anyway, its occupancy bound may be less than
the original kernel; we make sure to use this occupancy bound as the
number of workgroups for the original kernel in order to compare
relevant execution times. \HEComment{Do we need to mention the
  possible occupancy reduction as an overhead?}

\paragraph{Results} \ADComment{Discuss the results.}
\mytab~\ref{tab:overhead} lists overhead slowdown ratios, both
geometric mean and maximum value. The overhead is below a 2 times
slowdown even in the worst case. We consider these results as
acceptable, given that our SVM-based scheduler performance is likely a
far upper bound of what a scheduler implemented directly in the
runtime could offer.

>>>>

\HEComment{I consider that the reason why we need SVM fine grain and
  atomics is discussed in the implementation section}

@@

\HEComment{given the paper title, maybe ``non-blocking'' would be more
  appropriate than ``non-persistent''? Or ``non-cooperative'' ?}

@@

\paragraph{Results}
\mytab~\ref{tab:nonpersistentworkload} illustrates the caracteristics
found for the three types of workloads. For the medium and heavy
workloads, the 40ms period corresponds to an execution every $25^{th}$
of seconds which coincide with the human persistence of vision. The
3ms execution duration of both light and medium configurations may
indicate a lower bound of GPU execution time for system workloads.

@@

@@

\paragraph{Experimental setup}
Cooperative scheduling primitives entails an overhead even if no
killing, forking or resizing ever happen. We measure this overhead via
the execution time ratio between the original kernel and the
cooperative one, forcing the scheduler to never modify the number of
active workgroups. Since the cooperative kernel contains the
non-persistent task code anyway, its occupancy bound may be less than
the original kernel; we make sure to use this occupancy bound as the
number of workgroups for the original kernel in order to compare
relevant execution times. \HEComment{Do we need to mention the
  possible occupancy reduction as an overhead?}

\paragraph{Results}
\mytab~\ref{tab:overhead} lists overhead slowdown ratios, both
geometric mean and maximum value. The overhead is below a 2 times
slowdown even in the worst case. We consider these results as
acceptable, given that our SVM-based scheduler performance is likely a
far upper bound of what a scheduler implemented directly in the
runtime could offer.
